### 2024-02-17 documentation/thesis/thesis_document.tex
.

As the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri} research and
applications, articulates the research question driving this thesis and
delineates the anticipated use cases and benefits that will be explored
and analysed throughout the study.

@@

Magnetic Resonance Imaging \gls{mri} stands as a cornerstone in clinical
diagnostics, utilizing the principles of nuclear magnetic resonance
\gls{nmr} to generate cross-sectional black-and-white images of the
body. This indispensable method plays a central role in contemporary
medicine and research, contributing significantly to saving lives.
Despite its widespread use, traditional \gls{mri} systems often rely on
large, heavy, and expensive magnets to achieve the necessary homogeneity
of the magnetic field for accurate imaging. \cite{Nitz2016}

Various types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electro magnets are energized by electrical currents, and
superconducting electro magnets produce magnetic fields through electric
induction. Regardless of the type, the primary objective is to create a
homogeneous magnetic field within the \gls{mri}. The higher the
homogeneity, the more accurate the measurements. This uniform magnetic
field aligns the molecules within the body or object, setting the stage
for a second magnetic system to stimulate these molecules for
spin-measurements.

@@

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While typically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviours and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\cite{OReilly2019-rn} have already demonstrated low-cost and
small-scale implementations with low-field \gls{mri} in 2021 calculating
images of a head successfully.

Permanent magnets, usually arranged in a circular ``Halbach array''
inside the \gls{mri}, are commonly used in low-field systems. However,
their drawback is the inherent variability in strength, complicating the
achievement of a homogeneous field and requiring precise strength
information for correct magnet ordering and \gls{mri} construction.

@@

This research initiative contributes to the improvement of low-frequency
\gls{mri} systems by enhancing the accuracy of permanent magnet
characterisation. The outcomes of this thesis provides insights into the
selection and evaluation of sensors for future low-field \gls{mri}
research, ultimately contributing to advancements in medical imaging
technologies.

@@

Notably, the focus on high-field systems dominated discussions until
around 1991 when the possibility of constructing \gls{mri} machines with
lower magnetic field strengths came up. This marked a shift in exploring
the potential advantages and applications of low-field \gls{mri}
systems. \cite{Nitz2016}

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field \gls{mri}-systems measured between
\emph{0.1T} and \emph{0.3T} compared to the usual \emph{1.5T} to
\emph{3T} and above in high-field \gls{mri} scanners
\cite{Hori2021-pt}.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri}s is the improved
imaging of soft material, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \cite{Hori2021-pt}, cost reduction, a smaller device
footprint, alleviated safety concerns and leading to diminished image
resolution within clinically feasible scan durations.
\cite{Arnold2023-cn}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
a limited \gls{snr} due to the constrained field strength.
\cite{Nitz2016}

@@

The positioning of permanent magnets holds an important role in
constructing an \gls{mri} and is influencing the homogeneity of the
\emph{B0} magnetic field. Halbach ring magnets
\cite{Halbach1980DesignOP} have become a common design for low field
\gls{mri} and \gls{nmr} systems \cite{cmr.a.20165}.

This positioning has the ability to generate extremely homogeneous
magnetic flux densities, produce virtually no stray fields and is
particularly attractive for larger magnets as their design has the best
flux-to-mass ratio \cite{Wickenbrock_2021}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \cite{inbook}
\end{itemize}

@@

Halbach magnetic arrays present a choice for mobile \gls{nmr} due to
their ability to produce highly homogeneous and robust magnetic fields
per unit of magnetic mass, coupled with minimal stray fields. The term
``Halbach Array'' (commonly known as ``magic rings'') denotes a precise
configuration of permanent magnets designed to amplify magnetic flux on
one side while concurrently mitigating or eliminating it on the opposite
side. \cite{inbook}

The Halbach magnetic array appears as a essential element for future
Magnet characterisation. Based on this fact this thesis centres on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

The shimming process is a essential step in magnetic resonance imaging
\gls{mri} to ensure homogeneous magnetic fields for precise imaging.
Shimming corrects irregularities in the static magnetic field that can
be caused by external influences or internal system errors. This process
optimizes field homogeneity, which is essential for high-resolution and
artifact-free images \cite{10.3389/fphy.2021.704566}.

Optimal homogeneity is attained through intricate designs facilitating
active shimming, a technique essential for achieving high-resolution
spectroscopy. Beyond this, simpler combinations and adaptations of
Halbach rings offer versatility, making them suitable for variable field
magnets or magnets that can be effortlessly opened without applying
force. \cite{inbook}

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field. Software
shimming, on the other hand, uses algorithms to adjust the control
parameters of the \gls{mri} system and improve homogeneity
\cite{10.3389/fphy.2021.704566}.

@@

According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
\cite{Nitz2016}

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\cite{OReilly2019-rn} in 2019.This innovative setup is subsequently
employed in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \cite{OReilly2021-ep}. In
2023, de Vos, Remis and Webb published a summary of the design of a
point-of-care Halbach array low-field \gls{mri} system
\cite{De_Vos2023-pb}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \cite{OReilly2019-rn} in 2019.
This innovative setup is subsequently employed in 2020 to acquire in
vivo MR images, showcasing the practical applications of their
pioneering research \cite{OReilly2021-ep}. In 2023, de Vos, Remis
and Webb published a summary of the design of an oint-of-care halbach
array low-field \gls{mri} system \cite{De_Vos2023-pb}.

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets and individual measuring points are
recorded. This data is then evaluated in separate software
\cite{Wickenbrock_2021}.

@@

This form of data processing of previously characterised magnetic data
is currently being implemented experimentally in projects using various
algorithms \cite{Wickenbrock_2021}. Standard sorting algorithms are
used as well as specialized algorithms for optimizing homogeneity by
rotating the individual magnets in a Halbach ring relative to each other
\cite{HalbachMRIDesigner}.

@@

Special algorithms from various projects are used to optimize
homogeneity. The challenge here is to ensure the seamless integration
and compatibility of these algorithms into the overall process. This
should make it possible to create a workflow from the individual magnet
to the finished optimized \gls{cad} model of a halbach ring.

@@

In addition \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below 1000\gls{ppm}. While O'Reilly,
Teeuwisse, and Webb were able to modify the ring diameter to influence
field homogeneity, the unique goal here is to characterize the magnets
pre-installation, allowing for proactive assessments of homogeneity
characteristics. This approach aims to provide insights into magnetic
field uniformity before the magnets are integrated, thereby streamlining
the optimisation process. Furthermore,

@@

The use cases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process \ref{use-case-evaluation}, the defined use cases are also used
as a reference to demonstrate the implemented capabilities of the
solution. This is essential for understanding the needs of the target
group and designing the end result accordingly.

@@

Once it is possible to record and store measured values, it should be
possible for the user to analyse and visualize this data using various
algorithms. The focus here should be on extending the framework with
user-created algorithms.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \textbf{User programmable data processing pipelines}
\end{enumerate}

@@

The flexibility to support different sensors and magnets makes the
system versatile and opens the possibility for use in different
applications. A low-cost magnetic field sensors interface will therefore
not only be economically attractive, but also facilitate the integration
of magnetic field sensors in different contexts.

@@

The selection process for possible magnetic field sensors initially
focussed on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

A key aspect of this selection is the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout
since these kind of sensors are easy to integrate compared to
non-digital sensors, which require specific frameworks. The integration
of integrated temperature sensors represents a significant enhancement
that will later enable precise temperature compensation.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Implemented digital magnetic field sensors
\label{Implemented_digital_magnetic_field_sensors.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

The table \ref{Implemented_digital_magnetic_field_sensors.csv} shows a
selection of sensors for which hardware and software support has been
implemented. The resolution of the selected sensors covers the expected
range of values required by the various magnets to be tested.

In the Evaluation \ref{evaluation} chapter, basic characterisation
methods are used to evaluate the sensors listed in
\ref{Implemented_digital_magnetic_field_sensors.csv} with regard to
their sensitivity and other parameters. This is done at this point, as
the components of the readout interface that enable interaction with the
sensors are considered first.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}
\caption{Mechanical components for the 1D sensor using 3D printed parts
\label{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png}}
\end{figure}

@@

The following figure
\ref{Mechanical_components_for_the_1D_sensor_using_3D_printed_parts.png},
shows a sectional view of the \gls{cad} drawing of the 1D-Single sensor
\ref{d-single-sensor}.

All parts are produced using the 3D printing additive manufacturing
processes. The sensor circuit board is glued underneath the magnet
holder. This is interchangeable, so different distances between sensor
and magnet can be realised.

The exchangeable magnetic holder (shown in green) can be adapted to
different magnets. It can be produced quickly due to the small amount of
parts used. The two recesses lock the magnet holder with the inserted
magnet over the sensor. The specified tolerances allow the magnet to be
inserted into the holder with repeat accuracy and without backlash. This
is important if several magnets have to be measured, where the
positioning over the sensor must always be the same.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_schematic_and_circuit_board.png}
\caption{1D sensor schematic and circuit board
\label{1D_sensor_schematic_and_circuit_board.png}}
\end{figure}

@@

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation.

All the necessary components and their circuitry are recorded on a
\gls{pcb} \ref{1D_sensor_schematic_and_circuit_board.png} and
subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s.

Special attention is paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and also offers options for later extensions. This
functionality opens up the possibility of synchronising data from
different sensors to achieve precise and coherent measurement results.
Overall, this integrated approach represents an effective solution for
the flexible evaluation of sensors and helps to optimise the development
process.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_structure.png}
\caption{Unified sensor firmware simplified program structure
\label{Unified_sensor_firmware_simplified_program_structure.png}}
\end{figure}

@@

The firmware is responsible for detecting the possible connected sensors
from table \ref{Implemented_digital_magnetic_field_sensors.csv} and
query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware is to be
integrated, only the required functions from listing
\ref{lst:CustomSensorClass} need to be implemented.

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor
{
public:
  CustomSensor();
  ~CustomSensor();
  // implement depending sensor communication interface
  bool begin(TwoWire& _wire_instance); // I2C
  bool begin(HardwareSerial& _serial_instance); // UART
  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
  // FUNCTIONS USED BY READOUT LOGIC
  bool is_valid() override;
  String capabilities() override;
  String get_sensor_name() override;
  bool query_sensor() override;
  sensor_result get_result() override;
};
#endif
\end{lstlisting}

The figure
\ref{Unified_sensor_firmware_simplified_program_structure.png} shows a
flow chart of the start process after powering on the sensor and the
subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

The used usb descriptor is a \gls{usb} \gls{cdc}. This is used to
emulate a virtual \emph{RS232} communication port using a \gls{usb} port
on a \gls{pc} and usually no additional driver is needed on modern host
systems.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number. This
ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time and are not out of sequence or
drift.

@@

All these steps are divided into different blocks with an editional
functionality for users to add own modules. This concept is explained in
the following chapter.

>>>>

In the following, the motivation for the development of this framework
is listed. The chapter provides a brief introduction into the problem
domain, delineates the scope and boundaries of the present research,
surveys the current state of the art in low-field \gls{mri} research and
applications, articulates the research question driving this thesis and
delineates the anticipated use cases and benefits that will be explored
and analysed throughout the study.

@@

\gls{mri} stands as a cornerstone in clinical diagnostics, utilizing the
principles of nuclear magnetic resonance \gls{nmr} to generate
cross-sectional black-and-white images of the body. This indispensable
method plays a central role in contemporary medicine and research,
contributing significantly to saving lives. Despite its widespread use,
traditional \gls{mri} systems often rely on large, heavy, and expensive
magnets to achieve the necessary homogeneity of the magnetic field for
accurate imaging. \customcite{NK16}

Various types of magnets are applicated in different \gls{mri} systems.
Permanent magnets generate a steady yet relatively weak magnetic field,
electromagnets are energized by electrical currents and superconducting
electromagnets produce magnetic fields through electric induction.
Regardless of the type, the primary objective is to create a homogeneous
magnetic field within the \gls{mri}. The higher the homogeneity, the
more accurate the measurements. Homogeneity in composed \gls{mri} can be
adapted using the shimming procedure which requires a lot of effort and
is prone to errors. This uniform magnetic field aligns the molecules
within the body or object, setting the stage for a second magnetic
system to stimulate these molecules for spin-measurements.

@@

In response to this, there is a growing interest in developing low-field
\gls{mri} systems that utilize in many cases permanent magnets. These
systems, while offering advantages in energy efficiency and reduced
complexity, face a significant challenge related to the inherent
variability in the strength of permanent magnets. Achieving homogeneity
in the magnetic field is crucial for accurate imaging or comparative
analyses. While typically calculated images have lower resolution due to
lower magnetic field strength, low-field systems facilitate the
comparison of different field behaviours and the identification of all
kinds of irritations. O'Reilly and Teeuwisse and de Gans
\customcite{OTW19} have already demonstrated low-cost and small-scale
implementations with low-field \gls{mri} in 2021 calculating images of a
head successfully.

Permanent magnets, usually arranged in a circular \emph{Halbach array}
inside the \gls{mri}, are commonly used in low-field systems. However,
their drawback is the inherent variability in strength, complicating the
achievement of a homogeneous field and requiring precise strength
information for correct magnet ordering and \gls{mri} construction.

@@

This research initiative contributes to the improvement of low-frequency
\gls{mri} systems by enhancing the accuracy of permanent magnet
characterisation. The outcome of this thesis provides insights into the
selection and evaluation of sensors for future low-field \gls{mri}
research, ultimately contributing to advancements in medical imaging
technologies.

@@

Notably, the focus on high-field systems dominated discussions until
around 1991 when the possibility of constructing \gls{mri} machines with
lower magnetic field strengths came up. This marked a shift in exploring
the potential advantages and applications of low-field \gls{mri}
systems. \customcite{NK16}

Low-field magnetic resonance imaging (low-field \gls{mri}) is a
\gls{mri} technique that operates at a lower magnetic field strength
compared to conventional high-field \gls{mri} scanners. Typically, the
magnetic field in low-field \gls{mri}-systems measured between
\emph{0.1T} and \emph{0.3T} compared to the usual \emph{1.5T} to
\emph{3T} and above in high-field \gls{mri} scanners \customcite{HH21}.

This technology is used in medical imaging as well as in preclinical
research. The main advantage of low-field \gls{mri}s is the improved
imaging of soft material, especially when examining joints and muscles.
It also offers more cost-effective alternatives to high-field \gls{mri}
systems \customcite{HH21}, cost reduction, a smaller device footprint,
alleviated safety concerns and leading to diminished image resolution
within clinically feasible scan durations. \customcite{AFL23}

Low-field \gls{mri} systems are predominantly composed of permanent
magnets. Through the connection of these permanent magnets, a consistent
magnetic field of up to \emph{0.35T} can be generated. However, this
achievement comes at the cost of an average system weight of \emph{14t}.
Despite their cost-effectiveness in production and maintenance,
permanent magnets show drawbacks such as high temperature dependence and
a limited \gls{snr} due to the constrained field strength.
\customcite{NK16}

@@

The positioning of permanent magnets holds an important role in
constructing an \gls{mri} and is influencing the homogeneity of the
\emph{B0} magnetic field. Halbach ring magnets \customcite{H80} have
become a common design for low field \gls{mri} and \gls{nmr} systems
\customcite{SB10}.

This positioning has the ability to generate extremely homogeneous
magnetic flux densities, produce virtually no stray fields and is
particularly attractive for larger magnets as their design has the best
flux-to-mass ratio \customcite{WZC21}.

@@

\begin{itemize}
\item
  \textbf{Material}: The magnetic properties of a material influence the
  generated field strength. Different materials have different magnetic
  susceptibilities.
\item
  \textbf{Magnetization}: The orientation of the magnetic moments in the
  material influences the field strength. A higher magnetization leads
  to a stronger field strength.
\item
  \textbf{Temperature}: Temperature can influence the magnetic
  properties of a material. The magnetization of some materials
  decreases with increasing temperature.
\item
  \textbf{Manufacturing process}: The manufacturing process can
  influence the magnetic properties of the material. This is dependent
  on the purity of the starting materials used and the processing
  methods. There may also be deviations in field strength if different
  magnets from different production batches are compared.
  \customcite{BC16}
\end{itemize}

@@

Halbach magnetic arrays present a choice for mobile \gls{nmr} due to
their ability to produce highly homogeneous and robust magnetic fields
per unit of magnetic mass, coupled with minimal stray fields. The term
\emph{Halbach Array} (commonly known as \emph{magic rings}) denotes a
precise configuration of permanent magnets designed to amplify magnetic
flux on one side while concurrently mitigating or eliminating it on the
opposite side. \customcite{BC16}

The Halbach magnetic array appears as an essential element for future
Magnet characterisation. Based on this fact this thesis centres on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

The shimming process is an essential step in \gls{mri} to ensure
homogeneous magnetic fields for precise imaging. Shimming corrects
irregularities in the static magnetic field that can be caused by
external influences or internal system errors. This process optimizes
field homogeneity, which is essential for high-resolution and
artifact-free images \customcite{WAH21}.

Optimal homogeneity is attained through intricate designs facilitating
active shimming, a technique essential for achieving high-resolution
spectroscopy. Beyond this, simpler combinations and adaptations of
Halbach rings offer versatility, making them suitable for variable field
magnets or magnets that can be effortlessly opened without applying
force. \customcite{BC16}

The sources for the shimming process can be hardware and software based.
Hardware shimming involves the use of gradient and radio frequency coils
that are specifically placed to align the magnetic field.
\customcite{BPA22} Software shimming, on the other hand, uses algorithms
to adjust the control parameters of the \gls{mri} system and improve
homogeneity \customcite{WAH21}.

@@

According to Wolfgang R. Nitz in 2016, just \emph{13.4\%} of actively
used \gls{mri} systems are low-field \gls{mri} (\emph{66.6\% 1.5T
systems, 20\% 3.0 T system, 14.4\% low field with \textless0.5T}).
\customcite{NK16}

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\customcite{OTW19} in 2019.This innovative setup is subsequently employed
in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \customcite{OTW21}. In 2023, de
Vos, Remis and Webb published a summary of the design of a point-of-care
Halbach array low-field \gls{mri} system \customcite{DRW23}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \customcite{OTW19} in 2019. This
innovative setup is subsequently employed in 2020 to acquire in vivo MR
images, showcasing the practical applications of their pioneering
research \customcite{OTW21}. In 2023, de Vos, Remis and Webb published a
summary of the design of a point-of-care Halbach array low-field
\gls{mri} system \customcite{DRW23}.

@@

In order to measure the magnets individually, there are already
implementations that use different measurement methods to determine the
field strength of individual magnets and individual measuring points are
recorded. This data is then evaluated in separate software
\customcite{WZC21}.

@@

This form of data processing of previously characterised magnetic data
is currently being implemented experimentally in projects using various
algorithms \customcite{WZC21}. Standard sorting algorithms are used as
well as specialized algorithms for optimizing homogeneity by rotating
the individual magnets in a Halbach ring relative to each other
\customcite{MWO24}.

@@

Special algorithms from various, public projects are used to optimize
homogeneity, like a genetic algorithms which O'Reilly implemented
\customcite{O24}. Therefore, the challenge is to ensure the seamless
integration and compatibility of these algorithms into the overall
process. This should make it possible to create a workflow from the
individual magnet to the finished optimized \gls{cad} model of a Halbach
ring.

@@

In addition, \emph{DeLoRI} efforts to achieve heightened accuracy,
striving for precision levels below 1000\gls{ppm}. While O'Reilly,
Teeuwisse, and Webb were able to modify the ring diameter to influence
field homogeneity, the unique goal at this point is to characterize the
magnets pre-installation, allowing for proactive assessments of
homogeneity characteristics. This approach aims to provide insights into
magnetic field uniformity before the magnets are integrated, thereby
streamlining the optimisation process. Furthermore,

@@

The use cases are defined in the course of project planning and provide
an overview of how the user interacts with the project and what
functionalities can be expected. In the later accomplished evaluation
process in chapter \ref{use-case-evaluation}, the defined use cases are
also used as a reference to demonstrate the implemented capabilities of
the solution. This is essential for understanding the needs of the
target group and designing the end result accordingly.

@@

Once it is possible to record and store measured values, it should be
possible for the user to analyse and visualize this data using various
algorithms. The focus at this point should be on extending the framework
with user-created algorithms.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \textbf{User-programmable data processing pipelines}
\end{enumerate}

@@

The flexibility to support different sensors and magnets makes the
system versatile and opens the possibility for use in different
applications. A low-cost magnetic field sensors interface will therefore
not only be economically attractive, but also facilitate the integration
of magnetic field sensors in different contexts like for compasses or
other devices.

@@

The selection process for possible magnetic field sensors initially
focisses on the most common and cost-effective ones, especially those
that are already used in smartphones and are therefore widely available.

A key aspect of this selection is the preference for sensors with
digital interfaces to facilitate implementation in the circuit layout
since these kinds of sensors are easy to integrate compared to
non-digital sensors, which require specific frameworks. The integration
of integrated temperature sensors represents a significant enhancement
that will later enable precise temperature compensation.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{List of in unified firmware implemented digital magnetic field
sensors with focus on different sensor capabilities
\label{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & HMC5883L & MMC5603NJ & AS5510\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D & 3D & 1D\tabularnewline
Temperature-Sensor & yes & no & yes & no\tabularnewline
Resolution {[}uT{]} & 98 & 0.2 & 0.007 & 48\tabularnewline
Range {[}mT{]} & ±130.0 & ±0.8 & ±3 & ±50\tabularnewline
Interface & \gls{i2c} & \gls{i2c} & \gls{i2c} & \gls{i2c}\tabularnewline
\bottomrule
\end{longtable}

The table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
shows a selection of sensors for which hardware and software support has
been implemented. The resolution of the selected sensors covers the
expected range of values required by the various magnets to be tested.

In the \emph{Evaluation} in chapter \ref{evaluation} basic
characterisation methods are used to evaluate the sensors listed in
table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
with regard to their sensitivity and other parameters. This is done at
this point, as the components of the readout interface that enable
interaction with the sensors are considered first.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}
\caption{Rendered mechanical structure of the 1D sensor \gls{cad} model
with different parts colored separately, and universal magnet mount
shown in green
\label{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png}}
\end{figure}

@@

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}.

All parts are produced using 3D printing additive manufacturing proces.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised.

The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets have to be
measured, where the positioning over the sensor must always be the same.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
\caption{1D sensor schematic using an Raspberry Pi Pico with a TLV493D
footprint in the center
\label{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}}
\end{figure}

@@

The focus is on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for basic operation. This not only enabled a time-saving implementation,
but also ensured a cost-efficient realisation. A \emph{Raspberry Pi
Pico} and a \emph{STM32F4} are used as an computer-sensor interface for
this thesis, which are populare, cost-effective and simple to implement.

All the necessary components and their circuitry are recorded on a
\gls{pcb} shown in figure
\ref{1D_sensor_schematic_using_an_Raspberry_Pi_Pico_with_a_TLV493D_footprint_in_the_center.png}
and subsequently manufactured. In addition, footprints are provided for
various sensor \gls{ic} packages. By placing mounting holes on the
\gls{pcb}, it is possible to attach various mechanical mounts on top of
the sensor \gls{ic}s. These hole are necessary for later adaptions and
sensor changes, such as different magnet holders or measurement
equipment (e.g.~temperature sensors).

Special attention is paid to the provision of an accessible
SYNC-\gls{gpio} connector. This enables subsequent multi-sensor
synchronization and also offers options for later sensor-extensions.
This functionality opens up the possibility of synchronising data from
different sensors to achieve precise and coherent measurement results.
Overall, this integrated approach represents an effective solution for
the flexible evaluation of sensors and helps to optimise the development
process.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
\caption{Unified sensor firmware program structure with listed setup and
main loop routines using simplified function blocks
\label{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}}
\end{figure}

@@

The firmware is responsible for detecting the possible connected sensors
shown in table
\ref{List_of_in_unified_firmware_implemented_digital_magnetic_field_sensors_with_focus_on_different_sensor_capabilities.csv}
and query measurements. This measured data can be forwarded to a host
\gls{pc} via a user interface and can then be further processed there.

An important component is that as many common sensors as possible can be
easily connected without having to adapt the firmware. This modularity
is implemented using abstract class design. These are initiated
according to the sensors found at startup. If new hardware needs to be
integrated, only the required functions in listing
\ref{lst:CustomSensorClass} need to be implemented.

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support into the unified sensor firmware package}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor
{
public:
  CustomSensor();
  ~CustomSensor();
  // implement depending sensor communication interface
  bool begin(TwoWire& _wire_instance); // I2C
  bool begin(HardwareSerial& _serial_instance); // UART
  bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
  // FUNCTIONS USED BY READOUT LOGIC
  bool is_valid() override;
  String capabilities() override;
  String get_sensor_name() override;
  bool query_sensor() override;
  sensor_result get_result() override;
};
#endif
\end{lstlisting}

The figure
\ref{Unified_sensor_firmware_program_structure_with_listed_setup_and_main_loop_routines_using_simplified_function_blocks.png}
shows a flow chart of the start process after powering on the sensor and
the subsequent main loop for processing the user commands and sensor
results. When the microcontroller is started, the software checks
whether known sensors are connected to \gls{i2c} or \gls{uart}
interfaces.

@@

The used usb descriptor is a (+usb)-\gls{cdc}. This is used to emulate a
virtual \emph{RS232} communication port using a \gls{usb} port on a
\gls{pc} and usually no additional driver is needed on modern host
systems.

@@

Ring buffers are well suited for applications with variable data rates
and minimise the need for complex memory management. The buffer can be
read out by command and the result of the measurement is sent to the
host. Each sensor measurement result is transmitted from the buffer to
the host together with a time stamp and a sequential number.

This ensures that in a multi-sensor setup with several sensors. The
measurements are synchronized in time like described in chapter
\ref{sensor-syncronisation-interface} and are not out of sequence or
drift.

@@

All these steps are divided into different blocks with an additional
functionality for users to add own modules. This concept is explained in
the following chapter.
